Analysis-ready VCF at Biobank scale using Zarr

### 2025-01-22 paper.tex

% Middle
\author[6]{Ben Jeffery} % https://orcid.org/0000-0002-1982-6801
\author[7]{Alistair Miles} % https://orcid.org/0000-0001-9018-4680
\author[8]{Sam Tallman} % https://orcid.org/0000-0001-7183-6276
\author[1]{Rafal Wojdyla} % https://orcid.org/0009-0005-0735-7090
\author[9]{Shadi Zabad} % https://orcid.org/0000-0002-8003-9284
\author[10]{Per Unneberg} % https://orcid.org/0000-0001-5735-3315

@@

\affil[1]{Related Sciences}
\affil[2]{The New Zealand Institute for Plant \& Food Research Ltd, Lincoln,
New Zealand}
\affil[3]{Department of Biochemistry, School of Biomedical Sciences, University of Otago, Dunedin, New Zealand}
\affil[4]{Independent researcher}
\affil[5]{Tom White Consulting Ltd.}
\affil[6]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, 
University of Oxford, UK}
\affil[7]{Wellcome Sanger Institute}
\affil[8]{Genomics England}
\affil[9]{School of Computer Science, McGill University, Montreal, QC, Canada}
\affil[10]{Department of Cell and Molecular Biology, National
  Bioinformatics Infrastructure Sweden, Science for Life Laboratory,
  Uppsala University, Uppsala, Sweden}

>>>>

% Middle, alphabetical order
\author[6]{Ben Jeffery} % https://orcid.org/0000-0002-1982-6801
\author[7]{Alistair Miles} % https://orcid.org/0000-0001-9018-4680
\author[8]{Sam Tallman} % https://orcid.org/0000-0001-7183-6276
\author[9]{Per Unneberg} % https://orcid.org/0000-0001-5735-3315
\author[1]{Rafal Wojdyla} % https://orcid.org/0009-0005-0735-7090
\author[10]{Shadi Zabad} % https://orcid.org/0000-0002-8003-9284

@@

\affil[1]{Related Sciences}
\affil[2]{The New Zealand Institute for Plant \& Food Research Ltd, Lincoln,
New Zealand}
\affil[3]{Department of Biochemistry, School of Biomedical Sciences, University of Otago, Dunedin, New Zealand}
\affil[4]{Independent researcher}
\affil[5]{Tom White Consulting Ltd.}
\affil[6]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, 
University of Oxford, UK}
\affil[7]{Wellcome Sanger Institute}
\affil[8]{Genomics England}
\affil[9]{Department of Cell and Molecular Biology, National
  Bioinformatics Infrastructure Sweden, Science for Life Laboratory,
  Uppsala University, Uppsala, Sweden}
\affil[10]{School of Computer Science, McGill University, Montreal, QC, Canada}
